Minimal trap spaces of Logical models are maximal siphons of their Petri net encoding

### 2022-05-12 cmsb22.tex
Large models observation

%%% For very huge models %%%
The third observation is that for very huge models (), the proposed method did not manage to finish the Petri net conversion before the timeout, as marked by ``???'' in Table~\ref{tab:result_real}.

>>>>

%%% For very huge models %%%
The third observation is that for very large models (i.e., more than two thousand nodes) the proposed method did not manage to finish the Petri net conversion before the timeout, as marked by ``???'' in Table~\ref{tab:result_real}.
This points to the fact that our current choice of using a BDD-based translation to obtain that Petri net encoding, though it provides a small/efficient ASP might be too costly to handle the largest models.
In such a case, a more \emph{naive} encoding might provide a much larger ASP program, with many redundant rules, but easier/faster to obtain.
The evaluation of the feasibility of such strategy, and of its impact on smaller instances, remains to be done and is out of the scope of this first article.
